The CMS Data Aggregation System

### 2010-05-04 doc/paper.tex
Next update: added intro to DAS section, new refs, etc.
git-svn-id: svn+ssh://svn.cern.ch/reps/CMSDMWM/DAS/trunk@645 4525493e-7705-40b1-a816-d608a930855b

%In a large modern enterprise, information is almost inevitably distributed among several database management systems. Despite considerable attention from the research community, relatively few commercial systems have attempted to address this issue. This article describes the technology that enables clients of IBM's federated database engine to access and integrate the data and specialized computational capabilities of a wide range of relational and non­relational data sources.

\begin{abstract}
%A meta-data plays significant role in a large modern enterprises, research experiments,
%digital libraries where it comes from different sources and distributed in a 
%variety of forms and digital formats. It is organized and managed by constantly
%evolving software using both relational and non-relational data sources. There is
%a big demand to enable information discovery from multiple sources.
%Here we discuss a new data aggregation system which consume and deliver information 
%from different relational and non-relational data sources on a concrete example 
%of large scale, distributed system of CMS physics experiment at LHC.

Meta-data plays signiﬁcant role in a large modern enterprises, 
research experiments and digital libraries where it comes from different 
sources and distributed in a variety of forms and digital formats. 
It is organized and managed by constantly evolving software using 
both relational and non-relational data sources. Even though we can apply
information retrieval approach to non-relation data sources,
we can't do so for relational ones, where information can be accessed via
pre-established set of data-services.
%Even though we can access it via set of data-services, twikies, blogs, etc.,
%the information discovery across them is still a manual task.
% which prevent
%information discovery
%there is no coherent way for information discovery from different sources
%in heterogeneous, distributed environment with different security policies enforced.

Here we discuss a new data aggregation system which consumes, 
indexes and delivers information from different relational and 
non-relational data sources to answer cross data-service queries 
and explore meta-data associated with petabytes of experimental data. 
We combine simplpicity of keyword-based search with precision of RDMS
under the new system. The aggregated information being collected from various sources,
allowing end-users to place dynamic queries, get precise answers and 
trigger information retrieval on demand. Such close to real-time system 
based on studies  of use cases of the CMS particle physics experiment at 
the LHC where we used a large scale, distributed computing system 
to motivate the work.

@@

\section{Introduction}
The European Organization for Nuclear Research, known as CERN, plays a leading
role in fundamental studies of physics. But it is also known as a place where
many innovations in the area of computer science were developed, e.g. World Wide Web.
Today, the Large Hadron Collider (LHC) at CERN is marking a new era of High Energy
Physics (HEP), promising to deliver a few PB of data each year. 
At this scale the ``information discovery'' within heterogeneous, distributed 
environment become a key ingredient of successful data analysis in HEP.
%scientists are facing with a new set of problems in an area of
%``information discovery'' within heterogeneous, distributed environment.
The data and associated meta-data are produced in variety of forms and digital formats.
They are stored and retrieved from relational and non-releational data-sources, such as 
RDMS systems, document oriented databases, blogs, twikies, file systems and
customized applications, etc. 
%Its access is restricted by broad variety of security 
%policies enforced by individual sites and community in general.
Working in such environment requires a lot of expertise and our users
(in this case physicists) are always looking for simple, intuitive and flexible
tool(s) to look-up their desired data. A well-known solutions, such as data-services
and search engines tighted to a specific data sources and end-users are left 
with a manual task to bookkeep and relatate information from them.

@@

\section{Related Work\label{RelatedWork}}
Even though the idea of keyword queries over the relational database(s)
%querying relation databases via keyword based search
%algorithms 
is not knew it is still under discussion in computer science domain.
A few alternative solutions has been proposed to address this issue
in last several years. In \cite{DBXplorer} the conjunctive keyword queries,
i.e. retrieval of only documents that contain all query keywords, has
been discussed. It requires that all keywords are matched in a row from
single table or joined tables. While \cite{QueryAnswer} make a step forward
by considering information around matched values and presents customized answers to
end-users over the generated new database. Those and other works\footnote{
For more information about
keyword based search over relational databases we redirect users to reference in
\cite{DBXplorer, QueryAnswer}.} 
are based on some kind of the graph over the underlying database and
moreover use a generated database out of the pristine one.
The proximity of the results in those techniques 
are mostly confined to the text-based values stored in a database, since the
keyword based search with numerical values 
need the precise knowledge of the related entity in a schema. For example, typing
100 can lead to inappropriate matches, such as row ids, and in order to be
answered correctly it requires additional keyword, clarifying its context, 
which should be matched with particular
entity (table.column) in the underlying database.
Therefore such approaches cannot be used to answer the logical questions, such as  
{\it find me total number of files whose size more then 20 but less then 
100 taken from january to february of 2009} which can be easily accomplished
using SQL syntax.

To address those limitations an attempt to build a simple, intuitive and 
flexible query language was introduced in \cite{DBS-QL}\footnote{A similar but less
sophisticated approach was done in \cite{AMI}}.
It represents a power of SQL while hiding underlying relational schema from 
the end-users. As a results a human questions were intuitively mapped into 
simple queries. For example, the question
{\it I'm looking for files who contain data taken on certain date and located at
particular site} was represented as simple as \cite{DBS-QL}
\begin{verbatim}
find file where date 2009-01-02 11:59 CET and site = T2
\end{verbatim}
This solution represents a common use cases within HEP community and provide
intuitive mapping between mental model of end-users and underlying database back-end.

At the same time the data aggregation is commonly addressed in the context of
federated databases, see for example \cite{FedDB}. It unifies data coming 
from different RDMS systems into federated DB where SQL queries can be placed to 
search desired data. Even though it would be interesting to apply technique 
discussed in \cite{DBS-QL} to a federated database it still requires 
an access to the underlying database schema. This obviously creates a problem
working in distributed heterogeneous environment where different security policies
are in place.

To avoid those limitations we decided to build a keyword-search based system around
existing data-services whose nature and access policies are defined by developers.
Keeping in mind that meta-data can come in different forms and data formats
we used a document-oriented database back-end with full support of query language.
The key ingredients were the setup of the mapping and analytics services which provide
necessary glue across existing API/notations and user queries. This approach 
allows us to perform the data aggregation across various data-services, achieve
precise answers using keyword-based queries
and organize information retrieval on demand.
%to store meta-data information 
%We wanted to expand this approach further and apply it 
%to handle cross data-service queries from broad variety 
%of relational and non-relational data-sources within 
%our distributed heterogeneous environment.

\section{CMS data model\label{DataModel}}
The CMS, Compact Muon Solenoid, \cite{CMS} 
is one of the two large general-purpose particle physics detectors built on 
the proton-proton Large Hadron Collider (LHC) at CERN in Switzerland and France. 
It is designed to explore the frontier of High Energy Physics and provide physicists
ability to look at conditions presented at early stage of our Universe.
More then 3000 physicists from 183 institutions reprepresenting almost 
38 countries are involved in the design, construction and maintenance of the experiment.

@@

\section{Data Aggregation System\label{DAS}}
The design of the DAS system was based on previous studies of CMS Data 
Bookkeeping System (DBS) \cite{DBS, DBS07}. We carefully analyzed user
requests and queries placed into the DBS, their patterns, frequencies and latency. 
As a result we created a data discovery service \cite{DD}. Originally it used MVC
architecture and later, being re-factored as pure presentation layer on top of 
the DBS Query Language (DBS-QL) \cite{DBS-QL} with support of dynamic queries against
DBS back-ends. The DBS-QL \cite{DBS-QL} syntax was based on SQL query language, where 
we took away relations and details on underlying schema from end-users. 
This was achieved by usaging Dijkstras shortest path algorithm 
to establish necessary table joins based on provided information in user queries and
knowledge of foreign key relationships from auto-loaded database schema.
The DBS-QL keys exposed to end-users were choosen based on a jargon used by
physicists. They're internally mapped into database entitites and attributes, 
e.g. the {\it run} DBS-QL key refers to run number attribute of run summary table.
A quick adoption and wide usage of DBS-QL gave us confidence in choosen approach 
and provide a basis for building DAS system.

@@

\noindent
Due to this set of requirements, we rule out the choice of RDMS as DAS back-ends
for several reasons. We agreed to support dynamic queries, data
aggregation on demand and pluggable data-services. Therefore a choice 
of concrete schema for data storage was problematic. Moreover we didn't impose
any transactions and data persistency in DAS. This allows us to look 
for alternative IT solutions.
Through the analysis of available options, such as a file-based and memory caches, 
key-value databases, documented-oriented databases we made our choice in favor 
of the last technology. Among them we evaluated CouchDB \cite{CouchDB} and 
MongoDB \cite{MongoDB}. Both systems provide schema free document
storage, replication and fail-over features, but our choice in favor of 
MongoDB was obvious, due to its support of dynamic queries, 
full indexies, including inner objects and embedded arrays,
and auto-sharding. Our prelimiary benchmarks shown that it can sustain
the desired load and size for our meta-data information. We used 
document-oriented database, MongoDB, as a back-end for the three 
main DAS components: Mapping, Analytics and DAS cache databases, 
which will be discussed next.

@@

Apart from previous DBS-QL syntax we decided to drop its syntax and allow users
express their queries in a free text-based form. Such queries were transformed 
into MongoDB query syntax, who was used internally in
DAS core layer. It represents a set of selection keys and conditions as a JSON document.
For example, a query
{\it dataset site=T1\_CH\_CERN}
where transformed into 
{\it \{"fields" : ["dataset"], "spec" : \{"site" : "T1\_CH\_CERN"\}\}}.
Such syntax was perfect fit for us, since it allows to store all queries
as JSON documents into Analytics DB for further analysis. It is worthwhile to note that
MongoDB query syntax is very reach. It supports advanced queries with 
boolean expressions, conditional operators, regular expressions, etc. providing
a real power for our end-users.

@@

\section*{References}
\begin{thebibliography}{9}
\bibitem{DBXplorer}
Sanjay Agrawal, Surajit Chaudhuri, Gautam Das: DBXplorer: A System for
Keyword-Based Search over Relational Databases. ICDE 2002: 5-16

\bibitem{QueryAnswer}
Georgia Koutrika, Alkis Simitsis, Yannis E. Ioannidis: Pr\'{e}cis: The Essence of
a Query Answer. ICDE 2006: 69-78

\bibitem{DBS-QL} V. Kuznetsov, D. Riley, A. Afaq, V. Sekhri, Y. Guo, L. Lueking,
``The CMS DBS Query Language'', CHEP 2009

\bibitem{AMI}
Altas AMI web portal:
http://ami.in2p3.fr/opencms/opencms/AMI/www/Tutorial/AMIMediation.html

@@

\bibitem{CMS} CMS Collaboration R. Adolphi et al., The CMS experiment at the CERN LHC, JINST, 0803, S08004 (2008)

\bibitem{CMSDataModel} 
.Grandi, D.Stickland, L.Taylor et al., The CMS Computing Model, CERN-LHCC-2004- 035/G-083 (2004);
A. Fanfani et. al.,
``Distributed Analysis in CMS'', to be published in Journal of Grid Computing.

\bibitem{DBS} A. Afaq, et. al. ``The CMS Dataset Bookkeeping Service'', CHEP 2007 
J.Phys.Conf.Ser, 119, 072001 (2008)

\bibitem{DBS07} A. Dolgert, V. Kuznetsov, C. Jones, D. Riley, 
``A multi-dimensional view on information retrieval of CMS data'', CHEP 2007

@@

\bibitem{Arms}
C. R. Arms, W. Y. Arms, ``Mixed Content and Mixed Metadata 
Information Discovery in a Messy World'',
chapter from ``Metadata in Practice'', ALA Editions, 2004

@@

\bibitem{REST}
Fielding, Roy Thomas ``Architectural Styles and the Design of 
Network-based Software Architectures'', Doctoral dissertation, 2000,
University of California, Irvine

\bibitem{PhEDEx}
Rehn et. al.,
``PhEDEx high-throughput data transfer management system'', CHEP06, Mumbai, India.
R. Egeland et al., Data transfer infrastructure for CMS data taking, Proceedings of Science,
PoS(ACAT08)033 (2008) ;
L. Tuura et al., Scaling CMS data transfer system for LHC start-up, J.Phys.Conf.Ser, 119, 072030 (2008)

@@

\bibitem{DBSearch}
D. Konopnicki, O. Shmueli,
``Database-Inspired Search'', 
Proc. of the 31st VLDB Conference, 2005.
\end{thebibliography}

>>>>

\begin{abstract}
Meta-data plays signiﬁcant role in large modern enterprises, 
research experiments and digital libraries where it comes from a different 
sources and distributed in a variety of forms and digital formats. 
It is organized and managed by constantly evolving software using 
both relational and non-relational data sources. Even though we can apply
information retrieval approach to non-relation data sources,
we can't do so for relational ones, where information can be accessed via
pre-established set of data-services.

Here we discuss a new data aggregation system which consumes, 
indexes and delivers information from different relational and 
non-relational data sources to answer cross data-service queries 
and explore meta-data associated with petabytes of experimental data. 
We combine simplpicity of keyword-based search with precision of RDMS
under the new system. The aggregated information being collected from various sources,
allowing end-users to place dynamic queries, get precise answers and 
trigger information retrieval on demand. Such close to real-time system 
based on studies  of use cases of the CMS particle physics experiment at 
the LHC where we used a large scale, distributed computing system 
to motivate this work.

@@

\section{Introduction}
The European Organization for Nuclear Research, known as CERN, plays a leading
role in fundamental studies of physics. But it is also known as a place where
many innovations in the area of computer science were developed, e.g. World Wide Web.
Today, the Large Hadron Collider (LHC) at CERN is marking a new era of High Energy
Physics (HEP), promising to deliver a few PB of data each year. 
At this scale the ``information discovery'' within heterogeneous, distributed 
environment becomes a key ingredient of successful data analysis in HEP.
The data and associated meta-data are produced in variety of forms and digital formats.
They are stored and retrieved from relational and non-releational data-sources, such as 
RDMS systems, document oriented databases, blogs, twikies, file systems,
customized applications, etc. 
Working in such environment requires a lot of expertise and our users, physicists, 
are always looking for simple, intuitive and flexible
tool(s) to look-up their desired data. A well-known solutions, such as data-services
and search engines are tighted to a specific data sources and end-users are left 
with a manual task to bookkeep and relatate information from them.

@@

\section{Related Work\label{RelatedWork}}
Even though the idea of keyword queries over the relational database(s)
%querying relation databases via keyword based search
%algorithms 
is not knew it is still under discussion in computer science domain.
A few alternative solutions has been proposed to address this issue
in last several years. In \cite{DBXplorer} the conjunctive keyword queries,
i.e. retrieval of only documents that contain all query keywords, has
been discussed. It requires that all keywords are matched in a row from a
single table or joined tables. Authors of \cite{QueryAnswer} made a step forward
by considering information around matched values and presents customized answers to
end-users over the generated new database. These and other related 
works\footnote{For more information about keyword based search over relational 
databases we redirect users to references in \cite{DBXplorer, QueryAnswer}.} 
are based on some kind of the graph over the underlying database and
moreover use a generated database out of the pristine one.
The proximity of the results in those techniques 
are mostly confined to the text-based values stored in a database, since 
usage of numerical values in the input search field is mostly useless without 
knowledge of the context of the value. For example, typing a value 100 
in the search input field leads to plenty of inappropriate matches, 
such as row ids, and in order to be
answered correctly requires additional keyword, clarifying its meaning, 
which should be matched with particular
entity (table.column) in the underlying database.
Therefore to answer presicely the logical questions, such as  
{\it find me total number of files whose size more then 20 but less then 
100} would be hard or almost impossible using keyword search techniques discussed 
in \cite{DBXplorer, QueryAnswer}, while it can be easily accomplished
using SQL syntax.

To address those limitations an attempt to build a simple, intuitive and 
flexible query language was introduced in \cite{DBS-QL}.
It represents a power of SQL while hiding underlying relational schema from 
the end-users. As a results a human questions were intuitively mapped into 
simple queries. For example, the question
{\it I'm looking for files who contain data taken on certain date and located at
particular site} was represented as simple as \cite{DBS-QL}
\begin{verbatim}
find file where date 2009-01-02 11:59 CET and site = T2
\end{verbatim}
This solution represents a common use cases within HEP community and provide
intuitive mapping between mental model of end-users and underlying database schema.

At the same time the data aggregation is commonly addressed in the context of
federated databases, see for example \cite{FedDB}. It unifies data coming 
from different RDMS systems into the federated DB where SQL queries can be placed to 
search for desired data. Even though it would be interesting to apply technique 
discussed in \cite{DBS-QL} to a federated database it still requires 
an access to the underlying database schema. This obviously creates a problem
in distributed heterogeneous environment where different security policies
are in place.

To avoid those limitations we decided to build a keyword-search based system around
existing data-services whose nature and access policies are defined by developers.
Keeping in mind that meta-data can come in different forms and data formats
we used a document-oriented database back-end with full support of the query language.
The key ingredients were the setup of the mapping and analytics services which provide
necessary glue across existing API/notations and user queries. This approach 
allows us to perform the dynamic data aggregation across various data-services, achieve
precise answers using keyword-based queries
and organize information retrieval on demand.
%to store meta-data information 
%We wanted to expand this approach further and apply it 
%to handle cross data-service queries from broad variety 
%of relational and non-relational data-sources within 
%our distributed heterogeneous environment.

\section{CMS data model\label{DataModel}}
The CMS, Compact Muon Solenoid, \cite{CMS} 
is one of the two large general-purpose particle physics detectors built on 
the proton-proton Large Hadron Collider (LHC) at CERN in Switzerland and France. 
It is designed to explore the frontier of the High Energy Physics and provide physicists
ability to look at conditions presented at the early stage of our Universe.
More then 3000 physicists from 183 institutions reprepresenting almost 
38 countries are involved in the design, construction and maintenance of the experiment.

@@

\section{Data Aggregation System\label{DAS}}
The goal of the Data Aggregation System was to combine existing data-services
under one umrella, utilizing their access rules, APIs, security policies, etc., and
allowing users to perform queries against them. In contrast, approaches
discussed in \cite{DBXplorer, QueryAnswer, FedDB} are
enforced a publication step of data into a dedicated database 
or central repositories \cite{iRODS}. Quite often it is required
that data should be converted into uniform data formats in order enable
aggregation, see \cite{OpenArchive}. In DAS architecture the data are provided
by existing data-services and infrastructure, whose design, implementation and
security policies are left up to their developers. Therefore DAS does not requires
a data preservation and transaction capabilities. Instead DAS can be treated
as proxy or caching layer where information retrieval (data) are triggered dynamically
by user queries. Such infrastructure allows data sharing across different queries and
data aggregation using appropriate mapping. Below we discuss details of
DAS architecture.

\subsection{DAS architecture}
The design of the DAS system was based on previous studies of CMS Data 
Bookkeeping System (DBS) \cite{DBS, DBS07}. We carefully analyzed user
requests and queries placed into the DBS, their patterns, frequencies and latency. 
As a result we created a data discovery service \cite{DD}. Originally it used MVC
architecture and later, being re-factored as pure presentation layer on top of 
the DBS Query Language (DBS-QL) \cite{DBS-QL} with support of dynamic queries against
DBS back-ends. The DBS-QL \cite{DBS-QL} syntax was based on SQL query language, where 
we took away relations and details on underlying schema from end-users. 
This was achieved by using Dijkstras shortest path algorithm 
to establish necessary table joins based on provided information in user queries and
knowledge of foreign key relationships from auto-loaded database schema.
The DBS-QL keys exposed to end-users were choosen based on a jargon used by
physicists. They're internally mapped into database entitites and attributes, 
e.g. the {\it run} DBS-QL key refers to run number attribute of run summary table.
A quick adoption and wide usage of DBS-QL gave us confidence in choosen approach 
and provide a basis for building DAS system.

@@

\noindent
Due to this set of requirements, we rule out the choice of RDMS as DAS back-end(s)
for several reasons. We agreed to support dynamic queries, data
aggregation on demand and pluggable data-services. Therefore a choice 
of concrete schema for data storage was problematic. Moreover we didn't impose
any transactions and data persistency in DAS. This allows us to look 
for alternative IT solutions.
Through the analysis of available options, such as a file-based and memory caches, 
key-value databases, documented-oriented databases we made our choice in favor 
of the last technology. Among them we evaluated CouchDB \cite{CouchDB} and 
MongoDB \cite{MongoDB}. Both systems provide schema free document
storage, replication and fail-over features, but our choice in favor of 
MongoDB was obvious, due to its support of dynamic queries, 
full indexies, including inner objects and embedded arrays,
and auto-sharding. Our prelimiary benchmarks shown that it can sustain
the desired load and size for our meta-data information. We used 
document-oriented database, MongoDB, as a back-end for the three 
main DAS components: Mapping, Analytics and DAS cache databases, 
which will be discussed next.

@@

\subsection{DAS queries}
Apart from previous DBS-QL syntax we decided to drop its syntax and allow users
express their queries in a free text-based form. Although we must clarify its
meaning. We used a pre-defined set of keys known to DAS to describe common
entities of our data. For example, {\it dataset, file, block, run, event}. Those
names were used by our users in their daily work operations. So, by typing
{\it file} we didn't perform a string matching to ``file'' string, but rather
look-up all file objects in a DAS. Moreover each DAS key has a default attribute.
For intance, for {\it dataset, block, file} the default attribute 
was a {\it name}, while for {\it run} and {\it event} the default attribute was 
a {\it number}. This allows to specify key-value pair as simple as possible, e.g.
{\it run=123456}, which means run number 123456. At the same time a queyr 
key, e.g. {\it site} meant to look-up all site objects. Such ability
to use key-value pairs resolve ambiguity in object values. For instance,
specifying a run number as {\it run=123456} instruct system to resolve
data object with run equal to 123456 rather then other objects which may have
123456 values, e.g. event number or file size. At the same time, to complement
the stregth of the DAS we do plan to index data objects and add a keyword-based 
search later.

The free text-based queries were transformed into MongoDB query syntax, 
who was used internally by DAS. It represents a set of selection 
keys and conditions as a JSON document. For example, a query
{\it dataset site=T1\_CH\_CERN}
where transformed into 
{\it \{"fields" : ["dataset"], "spec" : \{"site" : "T1\_CH\_CERN"\}\}}.
Such syntax was perfect fit for us, since it allows to store all queries
as JSON documents into Analytics DB for further analysis. It is worthwhile to note that
MongoDB query syntax is very reach. It supports advanced queries with 
boolean expressions, conditional operators, regular expressions, etc. providing
a real power for our end-users.

@@

\section*{References}
\begin{thebibliography}{9}
\bibitem{DBXplorer}
S. Agrawal, S. Chaudhuri, G. Das,
``DBXplorer: A System for Keyword-Based Search over Relational Databases'',
ICDE 2002, pp. 5-16.

\bibitem{QueryAnswer}
G. Koutrika, A. Simitsis, Y. E. Ioannidis,
``Pr\'{e}cis: The Essence of a Query Answer'',
ICDE 2006, pp. 69-78.

\bibitem{DBS-QL} 
V. Kuznetsov, D. Riley, A. Afaq, V. Sekhri, Y. Guo, L. Lueking,
``The CMS DBS Query Language'', CHEP 2009.

%\bibitem{AMI}
%Altas AMI web portal,
%http://ami.in2p3.fr/opencms/opencms/AMI/www/Tutorial/AMIMediation.html

@@

\bibitem{CMS} 
R. Adolphi et al., 
``The CMS experiment at the CERN LHC'',
JINST 0803, S08004 (2008).

\bibitem{CMSDataModel} 
C. Grandi, D.Stickland, L.Taylor et al.,
``The CMS Computing Model'',
CERN-LHCC-2004-035/G-083 (2004);
A. Fanfani et. al., 
``Distributed Analysis in CMS'', 
to be published in Journal of Grid Computing.

\bibitem{iRODS}
The Integrated Rule-Oriented Data System,
http://www.irods.org/

\bibitem{OpenArchive}
Open Archives Initiative,
http://www.openarchives.org/

\bibitem{DBS} 
A. Afaq, et. al.,
``The CMS Dataset Bookkeeping Service'', 
J. Phys. Conf. Ser, 119, 072001 (2008).

\bibitem{DBS07} 
A. Dolgert, V. Kuznetsov, C. Jones, D. Riley, 
``A multi-dimensional view on information retrieval of CMS data'',
Journal of Physics: Conference Series 119, 072013, (2008).

@@

\bibitem{Arms}
C. R. Arms, W. Y. Arms,
 ``Mixed Content and Mixed Metadata 
Information Discovery in a Messy World'',
chapter from ``Metadata in Practice'', ALA Editions, 2004.

@@

%\bibitem{REST}
%Fielding, Roy Thomas ``Architectural Styles and the Design of 
%Network-based Software Architectures'', Doctoral dissertation, 2000,
%University of California, Irvine

\bibitem{PhEDEx}
Rehn et. al.,
``PhEDEx high-throughput data transfer management system'', CHEP 2006;
R. Egeland et al., 
``Data transfer infrastructure for CMS data taking'', 
Proceedings of Science, PoS (ACAT08) 033 (2008);
L. Tuura et al., 
``Scaling CMS data transfer system for LHC start-up'', 
J. Phys. Conf. Ser, 119, 072030 (2008).

@@

%\bibitem{DBSearch}
%D. Konopnicki, O. Shmueli,
%``Database-Inspired Search'', 
%Proc. of the 31st VLDB Conference, 2005.
\end{thebibliography}
